Why do we Eval?\\[2mm]\Large A large-scale study of Eval usage in R

### 2020-11-30 inst/paper/main.tex
Add one more

>>>>

In vcrpart package they use this a lot (following is just one instance):

\begin{lstlisting}
vcrpart::tvcglm <- function(formula, data, family,
                   weights, subset, offset, na.action = na.omit,
                   control = tvcglm_control(), ...) {
    mc <- match.call()
    mc[[1L]] <- as.name("tvcm")
    if (!"control" %in% names(mc))
        mc$control <- formals(tvcglm)$control
    if ("fit" %in% names(list(...)))
        warning("inputs for 'fit' in 'tvcglm' are ignored. ",
                "'fit' is set to 'glm'.")
    mc$fit <- "glm"
    return(eval.parent(mc))
  }
\end{lstlisting}

The examples above are related to the use of \c{match.call} whose documentation talks about these use cases:

\begin{verbatim}
‘match.call’ is most commonly used in two circumstances:

        • To record the call for later re-use: for example most
          model-fitting functions record the call as element ‘call’ of
          the list they return.  Here the default ‘expand.dots = TRUE’
          is appropriate.

        • To pass most of the call to another function, often
          ‘model.frame’.  Here the common idiom is that ‘expand.dots =
          FALSE’ is used, and the ‘...’ element of the matched call is
          removed.  An alternative is to explicitly select the
          arguments to be passed on, as is done in ‘lm’.
\end{verbatim}
